### 2017-03-06 readme.Rmd
Edit of README for JOSS.

## Usage 
Installing the package:
```{r install, eval=FALSE}
library(devtools)
install_github('lebebr01/highlightHTML')
```

@@

```{r function, eval=FALSE}
library(hightlightHTML)
highlight_html(input = "path/to/file", output = "path/to/saved/file", updateCSS = TRUE, tags = c("Vector of CSS code here"))
```

@@

>>>>

## Installation 
Installing the package:
```{r install, eval=FALSE}
install.packages("highlightHTML")
```

or the development version with devtools:
```{r devtools, eval = FALSE}
devtools::install_github('lebebr01/highlightHTMl')
```

## Usage

@@

```{r function, eval=FALSE}
library(hightlightHTML)
file <- system.file('examples', 'bgtable.html', 
                    package = 'highlightHTML')

tags <- c("#bgred {background-color: #FF0000;}", 
  "#bgblue {background-color: #0000FF;}")

highlight_html(input = file, 
               output = tempfile(fileext = ".html"), 
               tags = tags,
               update_css = TRUE, 
               browse = TRUE,
               print = FALSE)
```

@@

## Vignette
Additional examples can be found in the vignette called, The Basics. This file give more information and examples. The vignette should come with the package when installed from CRAN, however, if you are using the developmental version from GitHub, you may need to tell the installer to build the vignette directly:

```{r build_vignette, eval = FALSE}
devtools::install_github('lebebr01/highlightHTML', build_vignettes = TRUE)
```
